---
output:
  pdf_document: default
  word_document: default
  html_document: default
---
```{r,include=FALSE}
library(dplyr)
library(ggplot2)
library(lattice)
library(plyr)
library(Rmisc)
library(stringr)
library(tidyr)
library(rstan)
library(cowplot)
```


```{r setup}
getwd()
knitr::opts_knit$set(root.dir = "/home/shulai/Documents/exp1_data0/0")
knitr::opts_knit$set(root.dir ="C:/Users/naszh/Google Drive (shulai@iu.edu)/IUB/Shiffrin Lab/mix_experiment/exp1_data0/0")

rn=c("Block","Trial","Condition","OldNew","Setsize","Serpos","Lag",
  "Response","Correctness","RT","WhichProbe",
  paste("prob",seq(1,6),sep=""),"surveyq")
# read.table("cmvman1048.txt",head=FALSE,sep="",fill = TRUE,col.names = rn)
```

# Basic
```{r}
subnum=63
basen="cmvman"
```

#Functions
##load data
```{r}
ld=function(basen,subnum){
  for (i in 1:subnum){
    if(file.exists(paste(basen,i,".txt",sep=""))){
      # print(i)
      if (i==1){
        d=read.table(paste(basen,i,".txt",sep=""),
                     head=FALSE,sep="",fill = TRUE,col.names = rn)
        d=d %>% mutate(Subnum=i) #%>%
      #replace_na(list(surveyq=surveyq[length(surveyq)]))
    }    else{
      d0=read.table(paste(basen,i,".txt",sep=""),
                    head=FALSE,sep="",fill = TRUE,col.names = rn)
      d0=d0 %>% mutate(Subnum=i) #%>%
      #replace_na(list(surveyq=surveyq[length(surveyq)]))
      d=rbind(d,d0)
    }
     d=d%>% select(Subnum,everything()) %>% arrange(Subnum) %>% filter(RT>0)
  }
    }
  return(d)
}

```
##plot RT
```{r}
plot_rtall=function(d,tit){
  dase=summarySEwithin(data=d,measurevar = "RT",withinvars = c("Setsize","Correctness","OldNew","Condition"))
  # print(dase)
  da1se=subset(dase,Correctness==1)
  p1=ggplot(data=da1se,aes(Setsize,RT))+
  geom_point(aes(color=as.factor(OldNew),shape=as.factor(Condition),group=OldNew),size=5)+
  geom_line(aes(color=as.factor(OldNew),linetype=as.factor(Condition),
                group=interaction(OldNew,Condition)))+
  scale_color_manual(name="Old-New",#breaks=c(1,0),
                      labels=c(`1`="Old", `2`="New"),
                      values=c("#F23005","#CC984D"))+
  scale_shape_discrete(name="Condition",
                     labels = c(`1`="CMpos_s",`2`="CMpos_reg",`3`="CMneg_h",`4`="CMneg_l",`5`="vm"))+
  scale_linetype_discrete(name="Condition",
                     labels =c(`1`="CMpos_s",`2`="CMpos_reg",`3`="CMneg_h",`4`="CMneg_l",`5`="vm"))+
  ggtitle(paste("Mean CorrectRT - Set Size",tit))+
     theme_light()+
    ylim(700,1550)
  return(p1)
}
 plot_rtall(d,"")
```

##plot Correct
```{r}
plot_error=function(d,tit){
  da_p=summarySEwithin(data=d,measurevar = "Correctness",withinvars = c("Setsize","OldNew","Condition"))
  # da_p
  p1=ggplot(data=da_p,aes(Setsize,1-Correctness))+
    geom_point(aes(color=as.factor(OldNew),shape=as.factor(Condition),group=OldNew),size=5)+
    geom_line(aes(color=as.factor(OldNew),linetype=as.factor(Condition),
                  group=interaction(OldNew,Condition)))+
    scale_color_manual(name="Old-New",#breaks=c(1,0),
                        labels=c(`1`="Old", `2`="New"),
                        values=c("#F23005","#CC984D"))+
    scale_shape_discrete(name="Condition",
                       labels = c(`1`="CMpos_s",`2`="CMpos_reg",`3`="CMneg_h",`4`="CMneg_l",`5`="vm"))+
    scale_linetype_discrete(name="Condition",
                       labels = c(`1`="CMpos_s",`2`="CMpos_reg",`3`="CMneg_h",`4`="CMneg_l",`5`="vm"))+
    ggtitle(paste("Error Rate- Set Size - ",tit))+
    scale_y_continuous("Probability of Error")+
    theme_light()+
    ylim(0,0.3)
  return(p1)
  }
```

## mutate new condition
```{r}
creatnewc=function(dc){
  d0=dc %>% mutate(Condition=as.numeric(Condition)) %>%
  mutate(specondi=case_when( Condition %in% as.factor(1:4)~ Condition,
                                  Condition==5&OldNew==1 ~ 5, #c5=vm-old
                                  Condition==5&OldNew==2 ~ 6) ) %>%  #6~vm-new
  mutate(specondi=as.factor(specondi))
  return(d0)
}

```

##p blockwise
```{r}
plot_rtblockwise = function(d,tit){
  # d=dc
  dp3=creatnewc(d)%>% filter(Correctness==1)
  dp3=summarySEwithin(data=dp3, measurevar = "RT", withinvars = c("Block","Setsize","specondi"))

  Condition_n=c("CMpos_s","CMpos_reg","CMneg_h","CMneg_l","vm_old","vm_new");names(Condition_n)=as.character(1:6)
  
  p=ggplot(dp3,aes(Block,RT))+
    geom_point(aes(shape=Setsize,color=Setsize),size=5)+
    geom_line(aes(linetype=Setsize,color=Setsize,
                  group=interaction(Setsize)))+
    ggtitle(paste("Correct RT accross blocks -"),tit)+
    facet_wrap(specondi~.,
               labeller = labeller(specondi=Condition_n) ,ncol=3)+
    theme_light()+
    theme(text = element_text(size=20))#;p
               # labeller = label_both)
  return(p)



}

plot_rtblockwise2=function(d,tit){
    dp3=creatnewc(d) %>% filter(Correctness==1)
    dp34=summarySEwithin(data=dp3, measurevar = "RT", withinvars =
                        c("Block","specondi"))
    Condition_n=c("CMpos_s","CMpos_reg","CMneg_h","CMneg_l","vm_old","vm_new");names(Condition_n)=as.character(1:6)
  p=ggplot(dp34,aes(Block,RT))+
    geom_point(aes(color=specondi,shape=specondi),size=5)+
    geom_line(aes(color=specondi,
                  group=specondi,linetype=specondi))+
    scale_color_discrete(labels = Condition_n )+
    scale_linetype_discrete(labels = Condition_n )+
    scale_shape_discrete(labels = Condition_n )+
    ggtitle(paste("Correct RT accross blocks",tit))+
    theme_light()+
    theme(text = element_text(size=20))
  return(p)
}

plot_rtblockwise3=function(d,tit){
    dp3=creatnewc(d) %>% filter(Correctness==1)
    dp34=summarySEwithin(data=dp3, measurevar = "RT", withinvars =
                        c("Block","specondi","Setsize"))
    Condition_n=c("CMpos_s","CMpos_reg","CMneg_h","CMneg_l","vm_old","vm_new");names(Condition_n)=as.character(1:6)
  p=ggplot(dp34,aes(Block,RT))+
    geom_point(aes(color=specondi,shape=specondi),size=5)+
    geom_line(aes(color=specondi,linetype=specondi,
                  group=specondi))+
    scale_color_discrete(labels = Condition_n )+
    scale_linetype_discrete(labels = Condition_n )+
    scale_shape_discrete(labels = Condition_n )+
    ggtitle(paste("Correct RT accross blocks",tit))+
    theme_light()+
    theme(text = element_text(size=20))+
    facet_grid(Setsize~.,labeller = label_both)
  return(p)
}
```

##participant wise
```{r}
plot_rtblockpar=function(d,tit){
    dp3=creatnewc(dc) %>% filter(Correctness==1)
    dp34=summarySEwithin(data=dp3, measurevar = "RT", withinvars =
                        c("Block","specondi","Subnum"))
    Condition_n=c("CMpos_s","CMpos_reg","CMneg_h","CMneg_l","vm_old","vm_new");names(Condition_n)=as.character(1:6)
  p=ggplot(dp34,aes(Block,RT))+
    geom_point(aes(color=specondi))+
    geom_line(aes(color=specondi,
                  group=specondi))+
    scale_color_discrete(labels = Condition_n )+
    ggtitle(paste("RT correct accross blocks across participant"),tit)+
    facet_wrap(Subnum~.,ncol=6)+
    theme_light()
  return(p)
}
```

#load data
```{r}
d=ld(basen,subnum)
d=d%>%mutate_at(c("Setsize","OldNew","Condition"),as.factor)
d_n8=d%>%filter(Subnum>8)
```


##clean data 
```{r}
plot(density(d$RT),xlim=c(0,5000))

# d$Trial[d$RT>4000]
# 
# d[d$Trial<10,]

dc=d%>%filter(RT<5000&RT!=0)
a=(length(dc$Subnum)-length(d$Subnum) )
b=length(d$Subnum)
a/b
```


#Manipulation check
```{r}
  a=array()
  for(i in 1:10){
    a[i]=sum(d$WhichProbe==i)/sum(length(d$Block)) 
  }
a
```


```{r,echo=FALSE,include=FALSE}
aggregate(data=d,Correctness~Subnum,mean)
```

# Plor rt for correct rsponse
```{r}
# 
# p1=plot_rtall(d,"orignal")
# p2=plot_rtall(dc,"CLeaned data")
# p3=plot_rtall(filter(dc,Block>1),"block>1")
# plot_grid(p1,p2,p3)
# p1;p2;p3
# 
# 
# plot_rtall(filter(dc,Block>1),"block>1")



plot_rtall(filter(d,Block>1)," ")
plot_rtall(filter(d,Block>1&Subnum>8)," (Exclude first 8 people that I ran)")
# plot_rtall(filter(d,Block>2&Subnum>21),"block>2")
```


VM-New is weird, let's see what if block>2

##frequent inference
Want: 1-2 cmpos vs cm neg
      1-5 cmpos vs vm pos
      2-5 cmneg vs vm pos
```{r}
#make new condition variable for every conditions

dcmut=creatnewc(dc) %>% filter(Correctness==1,Block>2)

# Want: 1-2 cmpos vs cm neg
#       1-5 cmpos vs vm pos
#       2-5 cmneg vs vm pos
TukeyHSD(data=dcmut,aov(RT~specondi,data=dcmut))

```
#model selsect
```{r}
dcmut=creatnewc(dc) %>% filter(Correctness==1)
dcn=dcmut %>% mutate(condn=case_when( specondi==1 ~ "CM+spe_",
                                  specondi==2 ~ "CM+reg_",
                                  specondi==3 ~ "CM-h_",
                                  specondi==4 ~ "CM-l_",
                                  specondi==5 ~ "VM+_",
                                  specondi==6 ~ "VM-_"))%>%
  mutate(condn=as.factor(condn))
```

```{r}
md=lm(data=dcn,RT~Setsize*condn*OldNew)
md0=lm(data=dcn,RT~Setsize+condn)
anova(md0,md)
summary(md0)
step(md,direction="both")


TukeyHSD(data=dcn,aov(RT~condn+Setsize,data=dcn))
```





#plot correcness
```{r}

plot_error(d,"orignal")
# plot_error(dc,"CLeaned data")
plot_error(filter(dc,Block>1),"block>1")

plot_error(filter(d,Block>1)," ")
```
##freq 
Want: 1-2 cmpos vs cm neg\
      1-5 cmpos vs vm pos\
      2-5 cmneg vs vm pos\
```{r}
TukeyHSD(data=dcmut,aov(Correctness~specondi,data=dcmut))

```
```{r}

```


#plot RT- Blockwise

```{r}
# plot_rtblockwise(dc,"cleand")
# plot_rtblockwise2(dc,"cleand")
# plot_rtblockwise2(dc%>%filter(Setsize!=2),"Setsize>2")
# plot_rtblockwise3(dc,"of different set size")

plot_rtblockwise(filter(d)," ")
plot_rtblockwise2(filter(d)," ")

plot_rtblockwise(filter(d,Block>1)," ")
plot_rtblockwise2(filter(d,Block>1)," ")
plot_rtblockwise3(filter(d,Block>1),"of different set size")
```

```{r}
# head(d)

plot_rtblockwise(dc,"cleand")
plot_rtblockwise2(dc,"cleand")
plot_rtblockwise2(dc%>%filter(Setsize!=2),"Setsize>2")
plot_rtblockwise3(dc,"of different set size")

plot_rtblockwise(d,"orgid")
plot_rtblockwise2(d,"orgid")
plot_rtblockwise4=function(d,tit){
      dp3=creatnewc(d) %>% filter(Correctness==1)
    dp34=summarySEwithin(data=dp3, measurevar = "RT", withinvars =
                        c("Block","specondi","Setsize"))
    Condition_n=c("CMpos_s","CMpos_reg","CMneg_h","CMneg_l","vm_old","vm_new");names(Condition_n)=as.character(1:6)
  p=ggplot(dp34,aes(Block,RT))+
    geom_point(aes(color=specondi,shape=specondi),size=5)+
    geom_line(aes(color=specondi,linetype=specondi,
                  group=interaction(Block,Setsize)))+
    scale_color_discrete(labels = Condition_n )+
    scale_linetype_discrete(labels = Condition_n )+
    scale_shape_discrete(labels = Condition_n )+
    ggtitle(paste("Correct RT accross blocks",tit))+
    theme_light()+
    theme(text = element_text(size=20))+
    facet_grid(Setsize~Block,labeller = label_both)
  return(p)
}
# plot_rtblockwise4(dc,"of different set size,blocks")
```


#p-participant wise
```{r}
plot_rtblockpar(filter(d,Block>1)," ")
```

#FIT MODLE
r-stan give it a try
```{r}
model.script0="
data{
 int lag[N];
}
parameters{

}

model{
    for(j in 1:M){
      m[j]=lag[]
    }
}



"
  
  
```


#fill in surveyq
```{r}
sq_arr=array()
for(i in 1:subnum){
  d_slice=filter(d,Subnum==i)
  t_length=length(d_slice$Subnum)
  sq_arr=c(sq_arr,rep(d_slice$surveyq[t_length],t_length))
}
# sq_arr=
d_f=d%>%mutate(
  surveyq=sq_arr[-1]
)

# i=1
# d_slice=filter(d,Subnum==i)
# t_length=length(d_slice$Subnum);t_length
# d_slice$surveyq[t_length]
```

```{r}
d_f%>%filter(surveyq==1) %>%summary()
```

```{r}

    
d0=filter(d_f,Subnum>16)
# summary(as.factor(d0$surveyq))
p1=plot_rtall(filter(d0,surveyq==1),"(Noticed)")
# p2=plot_rtall(filter(d0,surveyq==2),"surveyq=yes_later")
p3=plot_rtall(filter(d0,surveyq==3),"(Didn't Notice)")
plot_grid(p1,p3)


p1=plot_error(filter(d0,surveyq==1),"(Noticed)")
# p2=plot_rtall(filter(d0,surveyq==2),"surveyq=yes_later")
p3=plot_error(filter(d0,surveyq==3),"(Didn't Notice)")
plot_grid(p1,p3)
```





































