---
output:
  pdf_document: default
  word_document: default
  html_document: default
---

# Load - setup
```{r,include=FALSE}
library(dplyr)
summarisedp=summarise
library(ggplot2)
library(lattice)
library(plyr)
library(Rmisc)
library(stringr)
library(tidyr)
# library(rstan)
# library(cowplot)
library(plotly)
library(wesanderson)
```

                

```{r setup}
getwd()
# knitr::opts_knit$set(root.dir = "/home/shulai/Documents/exp1_data0/0")
# knitr::opts_knit$set(root.dir ="C:/Users/naszh/Google Drive (shulai@iu.edu)/IUB/Shiffrin Lab/mix_experiment/SIDE exp/sidedata")
knitr::opts_knit$set(root.dir ="/home/shulai/Insync/shulai@iu.edu/Google Drive/IUB/Shiffrin Lab/mix_experiment/SIDE exp/sidedata")

rn=c("Block","Trial","Old","testcdisgard","Setsize","Serpos","Lag",
  "Response","Correctness","Side","RT","WhichProbe","Stimkind","FileCondi",
  paste("prob",seq(1,8),sep="")) #old: 1 old 2:new
# read.table("cmvman1048.txt",head=FALSE,sep="",fill = TRUE,col.names = rn)
```




#Functions
##load data function

```{r}
# ld=0

ld=function(basen,subnum,rn){
  imin=1000
  for (i in 1:subnum){
    if(file.exists(paste(basen,i,".txt",sep=""))){
      if (i<imin) imin=i
      # print(i)
      if (i==imin){
        d=read.table(paste(basen,i,".txt",sep=""),
                     head=FALSE,sep="",fill = TRUE,col.names = rn)
        d=d %>% mutate(Subnum=i) 
    }    else{
      d0=read.table(paste(basen,i,".txt",sep=""),
                    head=FALSE,sep="",fill = TRUE,col.names = rn)
      d0=d0 %>% mutate(Subnum=i) 
      d=rbind(d,d0)
    }
      d=d%>% select(Subnum,everything()) %>% arrange(Subnum) %>% 
        # filter(RT<4000,RT>180) %>%
        filter(Block>1)
  }
    }
  return(d)
}
# basen
# # ld
# read.table("PureANdebug22.txt",head=FALSE,sep="",fill = TRUE,col.names = rn)
# ld("PureANdebug10",1,rn)
```


##Load data
```{r}
d_cmat=ld("CMat",40,rn)
d_mix1=ld("MIX",40,rn) #%>% filter(Subnum>13)
d_mix2=ld("MIX2_",40,rn)#%>% filter(Subnum>13)
d_purean=ld("PureAN",40,rn)
d_purecm=ld("PureCM",40,rn)
d_purevm=ld("VMpure",40,rn)
d=rbind(d_cmat,d_mix1,d_mix2,d_purean,d_purecm,d_purevm)
d_my=ld("mydata",1,rn)
dx=d%>%group_by(Subnum,FileCondi) %>%dplyr::summarise(n())
summary(dx$FileCondi)
all_subnum=length(dx$Subnum)
all_subnum = paste("(N_total = ", all_subnum,")",sep="")


```
```{r}
sum(summary(dx$FileCondi) %>% as.data.frame())
sum(d$RT>4000)/dim(d)[1]
sum(d$RT>2000)/dim(d)[1]

d1=d %>%
  filter(RT>2000)%>%
  group_by(FileCondi) %>%
  dplyr::summarise(rtn1=n())%>%
  left_join( d %>%
  group_by(FileCondi) %>%
  dplyr::summarise(rtn2=n())) %>%
  mutate(prop = rtn1/rtn2)

d1


```

```{r}
dnow = dx$FileCondi %>% summary() %>% data.frame()
dnow$. %>% sum
```



```{r}


ave_rt = array(dim=length(d$Subnum))
ave_rt[d$Setsize==2] = mean(d$RT[d$Setsize==2])
data.frame(d,ave_rt)
```

```{r}
dnew = d %>% group_by(Setsize) %>% dplyr::summarise(rt_mean=mean(RT))
plot(dnew)
```


#Correct stuff
Correct till 14
### correct pure cm
```{r}
d_purecmc=d_purecm %>%
  mutate(WhichProbe = case_when(Subnum<=14 & Side==1 & Old ==1 ~ WhichProbe+8,
                                Subnum<=14 & Side==1 & Old==2 ~ WhichProbe-8,
                                TRUE ~ as.double(WhichProbe))) 
# %>%
#   # filter(Subnum==1) %>%
#   mutate(Old = case_when(Old==1 ~ "Old",
#                          Old==2 ~ "New"),
#          Side= case_when(Side==0 ~ "Left",
#                          Side==1 ~ "Right"))
# d_purecmc %>% select(Side,Old,WhichProbe,Serpos,16:23)
# d_purecm %>% select(Side,Old,WhichProbe,Serpos,16:23)
# names(d_purecm)

 # d_purecmc %>% 
 #   select(Subnum,Side,Old,WhichProbe) %>% 
 #   arrange(Subnum,WhichProbe,Old) %>%
 #   filter(WhichProbe==1)
 
# sum_check=d_purecmc %>% group_by(WhichProbe) %>%
#   filter(WhichProbe<9)%>%
#   dplyr::summarise(num_right=sum(Side=='Right'&Old=='New'),prob=num_right/n())
# sum_check
# sum_check$prob %>% mean()

d_purecmc%>%
  select(Old,Side,WhichProbe, Subnum)%>%
  mutate(Old = case_when(Old==1 ~ "Old",
                         Old==2 ~ "New"),
         Side= case_when(Side==0 ~ "Left",
                         Side==1 ~ "Right"))%>%
  mutate(check = case_when(
    Old=="New" & Side=="Right" & WhichProbe< 9 ~ "T",
    Old=="New" & Side=="Left"  & WhichProbe>=9 ~ "T",
    Old=="Old" & Side=="Right" & WhichProbe>=9 ~ "T",
    Old=="Old" & Side=="Left"  & WhichProbe< 9 ~ "T",
    TRUE ~ 'F')) %>%
  # filter(Subnum>14)
  group_by(Subnum) %>%
  dplyr::summarise(sum(check=="F"))
# 
# d_purecmc %>% group_by(WhichProbe) %>%
#   dplyr::summarise(prob_test=n()/length(d_purecmc$Subnum))%>%
#   mutate(sum=sum(prob_test))
# # m$prob_test %>%sum()
# names(d_purecmc)
# d_purecmc %>% group_by(Stimkind) %>%
#   dplyr::summarise(prob_test=n()/length(d_purecmc$Subnum))%>%
#   mutate(sum=sum(prob_test))

```
### Correct cmat
correct till 14
```{r}
d_cmatc = d_cmat %>%
  mutate(WhichProbe = case_when(Subnum<=14&Side == 1 & Old ==1& Stimkind==1 ~ WhichProbe+8,
                                Subnum<=14&Side == 1 & Old ==2 & Stimkind==1 ~ WhichProbe-8,
                                TRUE ~ as.double(WhichProbe)))
d_cmatc %>%
  # filter(Subnum==1) %>%
  select(WhichProbe,Old,Side,Stimkind,Subnum)  %>%
  mutate(Old = case_when(Old==1 ~ "Old",
                         Old==2 ~ "New"),
         Side= case_when(Side==0 ~ "Left",
                         Side==1 ~ "Right"),
         Stimkind = case_when(Stimkind==1 ~ "CM",
                              TRUE ~ "AN")) %>%

    filter(Stimkind=="CM")%>%
  mutate(check = case_when(
    Old=="New" & Side=="Right" & WhichProbe< 9 ~ "T",
    Old=="New" & Side=="Left"  & WhichProbe>=9 ~ "T",
    Old=="Old" & Side=="Right" & WhichProbe>=9 ~ "T",
    Old=="Old" & Side=="Left"  & WhichProbe< 9 ~ "T",
    TRUE ~ 'F'))%>% 
  group_by(Subnum)%>%
  dplyr::summarise(sum(check=="F"))
```
### correct mix1 (8)
correct till 15
```{r}
d_mix1c=d_mix1%>%
  mutate(WhichProbe = case_when(Subnum<=15 & Side==1 & Old==1 & WhichProbe<9 ~ WhichProbe+8,
                                TRUE ~ as.double(WhichProbe)))

d_mix1c %>%
  # filter(Stimkind==1)%>%
  # select(Old,Side,WhichProbe,Stimkind,Serpos,16:23)%>%
  select(Old,Side,WhichProbe,Subnum,Stimkind) %>%
  mutate(Old = case_when(Old==1 ~ "Old",
                         Old==2 ~ "New"),
         Side= case_when(Side==0 ~ "Left",
                         Side==1 ~ "Right"))%>%
  filter(Stimkind==1)%>%
  mutate(check = case_when(
    Old=="New" & Side=="Right" & WhichProbe< 9 & WhichProbe<17~ "T",
    Old=="New" & Side=="Left"  & WhichProbe>=9 & WhichProbe<17~ "T",
    Old=="Old" & Side=="Right" & WhichProbe>=9 & WhichProbe<17~ "T",
    Old=="Old" & Side=="Left"  & WhichProbe< 9 & WhichProbe<17~ "T",
    TRUE ~ 'F')) %>% 
  group_by(Subnum)%>%
  dplyr::summarise(sum(check=="F"))


d_mix1c %>% group_by(Side,Old)%>%
  dplyr::summarise(sum(n())/length(d_mix1c$ Subnum))
```

### Correct mix2 (4)
till 14
```{r}
d_mix2c=d_mix2%>%
  mutate(WhichProbe = case_when(Subnum<14 & Side==1 & Old==1 & WhichProbe<9 ~ WhichProbe+4,
                                TRUE ~ as.double(WhichProbe)))

d_mix2c %>%
  # filter(Stimkind==1)%>%
  # select(Subnum,Old,Side,WhichProbe,Stimkind)%>%
  mutate(Old = case_when(Old==1 ~ "Old",
                         Old==2 ~ "New"),
         Side= case_when(Side==0 ~ "Left",
                         Side==1 ~ "Right"))%>%
  filter(Stimkind==1)%>%
  mutate(check = case_when(

    Old=="New" & Side=="Right" & WhichProbe< 5 & WhichProbe<9~ "T",
    Old=="New" & Side=="Left"  & WhichProbe>=5 & WhichProbe<9~ "T",
    Old=="Old" & Side=="Right" & WhichProbe>=5 & WhichProbe<9~ "T",
    Old=="Old" & Side=="Left"  & WhichProbe< 5 & WhichProbe<9~ "T",
    TRUE ~ 'F')) %>% 
  group_by(Subnum)%>%
  dplyr::summarise(sum(check=="F"))


# d_mix2c %>% group_by(Stimkind,Old,Side) %>%
#   dplyr::summarise(n=n())
```


### **Rebinding stuff
```{r}
d=rbind(d_cmatc,d_mix1c,d_mix2c,d_purean,d_purecmc,d_purevm)
write.csv(d,"Grand_data.csv")
```

# Data cleaning
```{r}
d%>%
      filter(FileCondi=="MIX") %>%
      mutate(Stimkind = case_when(Stimkind==1 ~ "CM",
                                  Stimkind==0 ~ "AN",
                                  Stimkind==3 ~ "VM",
                                  TRUE ~ "Wrong")) %>%
      filter(Correctness==1) %>%
      group_by(Subnum, Stimkind) %>% 
      dplyr::summarise(rt_m=mean(RT))%>%
      arrange(rt_m)
```
```{r}
seq(1,length(levels(as.factor(d$Subnum))))
```

## *Clean_func()
```{r}
Clean_func = function(d, exclude, condi, is.rt, nsd=3){
  colors = wes_palette(names(wes_palettes[8]),n=64,type="continuous");colors=sample(colors,length(colors))
  grant_RTm = mean(d$RT)
  sdm = sd(d$RT)
  if (is.rt==1){
    dclean = d %>% 
      filter(! Subnum %in% exclude) %>% 
      filter(FileCondi==condi) %>%
      mutate(Stimkind = case_when(Stimkind==1 ~ "CM",
                                  Stimkind==0 ~ "AN",
                                  Stimkind==3 ~ "VM",
                                  TRUE ~ "Wrong")) %>%
      filter(Correctness==1) %>%
      group_by(Subnum, Stimkind) %>% 
      dplyr::summarise(rt_m=mean(RT),diff = rt_m-grant_RTm) %>%
      arrange(rt_m)
    dclean = dclean %>% 
      ungroup()%>%
      group_by(Stimkind)%>%
      arrange(Stimkind, rt_m) %>%
      mutate(order = row_number())
    # dclean = 
    ddat = dclean %>% group_by(Stimkind) %>% dplyr::summarise(mu3 = mean(rt_m),sd3 = sd(rt_m)/sqrt(n()))
    #%>%
      # mutate(tf=case_when(abs(grant_RTm - rt_m) > 2*sdm ~ "T",
                       # TRUE ~ "F"))'

    mean_wt <- data.frame(Stimkind = as.factor(levels(as.factor(dclean$Stimkind))), wtupper = nsd*ddat$sd3+ddat$mu3,
                          wtlower = ddat$mu3-nsd*ddat$sd3 )
    
    if(length(exclude)==0) exclude = "None"
    p=ggplot(dclean, aes(order,rt_m))+
      geom_point(aes(color=as.factor(Subnum)),alpha=0.2)+
      geom_text(aes(label=as.factor(Subnum),color=as.factor(Subnum)),hjust=0.4)+
      scale_color_manual(values = colors)+
      facet_grid(.~Stimkind)+
      geom_hline(aes(yintercept = wtupper),mean_wt)+
      geom_hline(aes(yintercept = wtlower),mean_wt)+
      guides(color=FALSE) +
      ggtitle(paste(" cRT:",condi, "- Exclude:", exclude,"- NumOfSdAway:", nsd))
  }
  else{
    dclean = d %>% 
      filter(! Subnum %in% exclude) %>% 
      filter(FileCondi==condi) %>%
      mutate(Stimkind = case_when(Stimkind==1 ~ "CM",
                                  Stimkind==0 ~ "AN",
                                  Stimkind==3 ~ "VM",
                                  TRUE ~ "Wrong")) %>%
      group_by(Subnum, Stimkind) %>% 
      dplyr::summarise(Error=mean(Correctness)) 
    dclean = dclean %>% 
      ungroup()%>%
      group_by(Stimkind)%>%
      arrange(Stimkind, Error) %>%
      mutate(order = row_number())
    
    ddat = dclean %>% group_by(Stimkind) %>% dplyr::summarise(mu3 = mean(Error),sd3 = sd(Error)/sqrt(n()))
    

    mean_wt <- data.frame(Stimkind = as.factor(levels(as.factor(dclean$Stimkind))), wtupper = nsd*ddat$sd3+ddat$mu3,
                          wtlower = ddat$mu3-nsd*ddat$sd3 )
    
    if(length(exclude)==0) exclude = "None"
    p=ggplot(dclean, aes(order,Error))+
      geom_point(aes(color=as.factor(Subnum)),alpha=0.4)+
      # geom_text(aes(label=paste(as.factor(Subnum),as.factor(Stimkind)),
      #               color=as.factor(Subnum)),hjust=0.4)+
      geom_text(aes(label=as.factor(Subnum),
                    color=as.factor(Subnum)),hjust=0.4)+
      scale_color_manual(values = colors)+
      facet_grid(.~Stimkind)+
      geom_hline(aes(yintercept = wtupper),mean_wt)+
      geom_hline(aes(yintercept = wtlower),mean_wt)+
      guides(color=FALSE)+
      ggtitle(paste(" Error:",condi, "- Exclude:", exclude,"- NumOfSdAway:", nsd))
  }
  
  return(p)
}
for(i in levels(d$FileCondi)){
  condiname = i
print(Clean_func(d,c(),condi=condiname,is.rt=1, nsd = 5))
print(Clean_func(d,c(),condi=condiname,is.rt=0, nsd = 5))
}

```

## clean_funcall
```{r}
Clean_funcall = function(d, exclude, func, is.rt, nsd=3){
  colors = wes_palette(names(wes_palettes[8]),n=64,type="continuous");colors=sample(colors,length(colors))
  grant_RTm = mean(d$RT)
  sdm = sd(d$RT)
  if (is.rt==1){
    dclean = d %>% 
      # filter(! Subnum %in% exclude) %>% 
      # filter(FileCondi==condi) %>%
      mutate(Stimkind = case_when(Stimkind==1 ~ "CM",
                                  Stimkind==0 ~ "AN",
                                  Stimkind==3 ~ "VM",
                                  TRUE ~ "Wrong")) %>%
      filter(Correctness==1) %>%
      group_by(FileCondi,Subnum, Stimkind) %>% 
      dplyr::summarise(rt_m=mean(RT),diff = rt_m-grant_RTm) %>%
      arrange(rt_m)
    dclean = dclean %>% 
      ungroup()%>%
      group_by(FileCondi, Stimkind)%>%
      arrange(FileCondi, Stimkind, rt_m) %>%
      mutate(order = row_number())%>%
      ungroup()
    # dclean = 
    ddat = dclean %>% group_by(Stimkind) %>% dplyr::summarise(mu3 = mean(rt_m),sd3 = sd(rt_m)/sqrt(n()))
    #%>%
      # mutate(tf=case_when(abs(grant_RTm - rt_m) > 2*sdm ~ "T",
                       # TRUE ~ "F"))'

    mean_wt <- data.frame(Stimkind = as.factor(levels(as.factor(dclean$Stimkind))), wtupper = nsd*ddat$sd3+ddat$mu3,
                          wtlower = ddat$mu3-nsd*ddat$sd3 )
    
    if(length(exclude)==0) exclude = "None"
    p=ggplot(dclean, aes(order,func(rt_m)))+
      geom_point(aes(color=as.factor(Subnum)),alpha=0.2)+
      geom_text(aes(label=as.factor(Subnum),color=as.factor(Subnum)),hjust=0.4)+
      scale_color_manual(values = colors)+
      facet_grid(FileCondi~Stimkind)+
      # geom_hline(aes(yintercept = wtupper),mean_wt)+
      # geom_hline(aes(yintercept = wtlower),mean_wt)+
      guides(color=FALSE) +
      ggtitle(paste(" cRT","- Exclude:", exclude,"- NumOfSdAway:", nsd))
  }
  else{
    dclean = d %>% 
      # filter(! Subnum %in% exclude) %>% 
      # filter(FileCondi==condi) %>%
      mutate(Stimkind = case_when(Stimkind==1 ~ "CM",
                                  Stimkind==0 ~ "AN",
                                  Stimkind==3 ~ "VM",
                                  TRUE ~ "Wrong")) %>%
      group_by(FileCondi,Subnum, Stimkind) %>% 
      dplyr::summarise(Error=1-mean(Correctness)) 
    dclean = dclean %>% 
      ungroup()%>%
      group_by(FileCondi,Stimkind)%>%
      arrange(FileCondi,Stimkind, Error) %>%
      mutate(order = row_number())
    
    ddat = dclean %>% group_by(Stimkind) %>% dplyr::summarise(mu3 = mean(Error),sd3 = sd(Error)/sqrt(n()))
    

    mean_wt <- data.frame(Stimkind = as.factor(levels(as.factor(dclean$Stimkind))), wtupper = nsd*ddat$sd3+ddat$mu3,
                          wtlower = ddat$mu3-nsd*ddat$sd3 )
    
    if(length(exclude)==0) exclude = "None"
    p=ggplot(dclean, aes(order,func(Error)))+
      geom_point(aes(color=as.factor(Subnum)),alpha=0.4)+
      # geom_text(aes(label=paste(as.factor(Subnum),as.factor(Stimkind)),
      #               color=as.factor(Subnum)),hjust=0.4)+
      geom_text(aes(label=as.factor(Subnum),
                    color=as.factor(Subnum)),hjust=0,vjust=-0.5 )+
      scale_color_manual(values = colors)+
      facet_grid(FileCondi~Stimkind)+
      # geom_hline(aes(yintercept = wtupper),mean_wt)+
      # geom_hline(aes(yintercept = wtlower),mean_wt)+
      guides(color=FALSE)+
      ggtitle(paste(" Error", "- Exclude:", exclude,"- NumOfSdAway:", nsd))
  }
  
  return(p)
}
Clean_funcall(d,c(),func = asin, is.rt=0, nsd = 5)
Clean_funcall(d,c(),func = identity, is.rt=1, nsd = 5)
```

# distribution
```{r}
dclean = d %>% 
  filter(! Subnum %in% exclude) %>% 
  filter(FileCondi==condi) %>%
  mutate(Stimkind = case_when(Stimkind==1 ~ "CM",
                              Stimkind==0 ~ "AN",
                              Stimkind==3 ~ "VM",
                              TRUE ~ "Wrong")) %>%
  group_by(Subnum, Stimkind) %>% 
  dplyr::summarise(Error=1-mean(Correctness)) 
dclean = dclean %>% 
  ungroup()%>%
  group_by(Stimkind)%>%
  arrange(Stimkind, Error) %>%
  mutate(order = row_number())

ggplot(dclean, aes(x=Error,fill  = as.factor(Stimkind))) +
  geom_density(alpha=0.5)

```


## clean_ss()


```{r}
Clean_ss = function(d, exclude, condi, is.rt){
  colors = wes_palette(names(wes_palettes[8]),n=37,type="continuous");#colors=sample(colors,length(colors))
  grant_RTm = mean(d$RT)
  sdm = sd(d$RT)
  if (is.rt==1){
    dclean = d %>% 
      filter(FileCondi==condi) %>%
      mutate(Stimkind = case_when(Stimkind==1 ~ "CM",
                                  Stimkind==0 ~ "AN",
                                  Stimkind==3 ~ "VM",
                                  TRUE ~ "Wrong")) %>%
      filter(Correctness==1) %>%
      group_by(Subnum, Stimkind,Setsize) %>% 
      dplyr::summarise(rt_m=mean(RT),diff = rt_m-grant_RTm) 
    
    ddat = dclean %>% group_by(Stimkind) %>% dplyr::summarise(mu3 = mean(rt_m),sd3 = sd(rt_m)/sqrt(n()))
    #%>%
      # mutate(tf=case_when(abs(grant_RTm - rt_m) > 2*sdm ~ "T",
                       # TRUE ~ "F"))'
    nsd = 5
    mean_wt <- data.frame(Stimkind = as.factor(levels(as.factor(dclean$Stimkind))), wtupper = nsd*ddat$sd3+ddat$mu3,
                          wtlower = ddat$mu3-nsd*ddat$sd3 )
    
    
    p=ggplot(dclean %>% filter(! Subnum %in% exclude)
           , aes(Subnum,rt_m))+
      geom_point(aes(color=as.factor(Subnum)),alpha=0.2)+
      geom_text(aes(label=as.factor(Subnum),color=as.factor(Subnum)),hjust=0.4)+
      scale_color_manual(values = colors)+
      facet_grid(Setsize~Stimkind)+
      # geom_hline(aes(yintercept = wtupper),mean_wt)+
      # geom_hline(aes(yintercept = wtlower),mean_wt)+
      guides(color=FALSE) +
      ggtitle(paste(" cRT-",condi, "exclude:", exclude))
  }
  else{
    dclean = d %>% 
      filter(FileCondi==condi) %>%
      mutate(Stimkind = case_when(Stimkind==1 ~ "CM",
                                  Stimkind==0 ~ "AN",
                                  Stimkind==3 ~ "VM",
                                  TRUE ~ "Wrong")) %>%
      group_by(Subnum, Stimkind, Setsize) %>% 
      dplyr::summarise(Error=mean(Correctness)) 
    
    ddat = dclean %>% group_by(Stimkind) %>% dplyr::summarise(mu3 = mean(Error),sd3 = sd(Error)/sqrt(n()))
    
    nsd = 5
    mean_wt <- data.frame(Stimkind = as.factor(levels(as.factor(dclean$Stimkind))), wtupper = nsd*ddat$sd3+ddat$mu3,
                          wtlower = ddat$mu3-nsd*ddat$sd3 )
    
    
    p=ggplot(dclean %>% filter(! Subnum %in% exclude)
           , aes(Subnum,Error))+
      geom_point(aes(color=as.factor(Subnum)),alpha=0.2)+
      geom_text(aes(label=as.factor(Subnum),color=as.factor(Subnum)),hjust=0.4)+
      scale_color_manual(values = colors)+
      facet_grid(Setsize~Stimkind)+
      # geom_hline(aes(yintercept = wtupper),mean_wt)+
      # geom_hline(aes(yintercept = wtlower),mean_wt)+
      guides(color=FALSE)+
      ggtitle(paste(" Error-",condi, "exclude:", exclude))
  }
  
  return(p)
}
Clean_ss(d,c(),condi="MIX",is.rt=1)
```

## Clean_old()
```{r}
Clean_old = function(d, exclude, condi, is.rt){
  colors = wes_palette(names(wes_palettes[8]),n=37,type="continuous");#colors=sample(colors,length(colors))
  grant_RTm = mean(d$RT)
  sdm = sd(d$RT)
  if (is.rt==1){
    dclean = d %>% 
      filter(FileCondi==condi) %>%
      mutate(Stimkind = case_when(Stimkind==1 ~ "CM",
                                  Stimkind==0 ~ "AN",
                                  Stimkind==3 ~ "VM",
                                  TRUE ~ "Wrong")) %>%
      mutate(Old = case_when(Old==1 ~ "Old",
                             Old==2 ~ "New")) %>%
      filter(Correctness==1) %>%
      group_by(Subnum, Stimkind,Old) %>% 
      dplyr::summarise(rt_m=mean(RT),diff = rt_m-grant_RTm) 
     
    ddat = dclean %>% group_by(Stimkind) %>% dplyr::summarise(mu3 = mean(rt_m),sd3 = sd(rt_m)/sqrt(n()))
    #%>% 
      # mutate(tf=case_when(abs(grant_RTm - rt_m) > 2*sdm ~ "T",
                       # TRUE ~ "F"))'
    nsd = 5
    mean_wt <- data.frame(Stimkind = as.factor(levels(as.factor(dclean$Stimkind))), wtupper = nsd*ddat$sd3+ddat$mu3,
                          wtlower = ddat$mu3-nsd*ddat$sd3 )
    
    
    p=ggplot(dclean %>% filter(! Subnum %in% exclude)
           , aes(Subnum,rt_m))+
      geom_point(aes(color=as.factor(Subnum)),alpha=0.2)+
      geom_text(aes(label=as.factor(Subnum),color=as.factor(Subnum)),hjust=0.4)+
      scale_color_manual(values = colors)+
      facet_grid(Old~Stimkind)+
      # geom_hline(aes(yintercept = wtupper),mean_wt)+
      # geom_hline(aes(yintercept = wtlower),mean_wt)+
      guides(color=FALSE) +
      ggtitle(paste(" cRT-",condi, "exclude:", exclude))
  }
  else{
    dclean = d %>% 
      filter(FileCondi==condi) %>%
      mutate(Stimkind = case_when(Stimkind==1 ~ "CM",
                                  Stimkind==0 ~ "AN",
                                  Stimkind==3 ~ "VM",
                                  TRUE ~ "Wrong")) %>%
      mutate(Old = case_when(Old==1 ~ "Old",
                             Old==2 ~ "New")) %>%
      group_by(Subnum, Stimkind, Old) %>% 
      dplyr::summarise(Error=mean(Correctness)) 
    
    ddat = dclean %>% group_by(Stimkind) %>% dplyr::summarise(mu3 = mean(Error),sd3 = sd(Error)/sqrt(n()))
    
    nsd = 5
    mean_wt <- data.frame(Stimkind = as.factor(levels(as.factor(dclean$Stimkind))), wtupper = nsd*ddat$sd3+ddat$mu3,
                          wtlower = ddat$mu3-nsd*ddat$sd3 )
    
    
    p=ggplot(dclean %>% filter(! Subnum %in% exclude)
           , aes(Subnum,Error))+
      geom_point(aes(color=as.factor(Subnum)),alpha=0.2)+
      geom_text(aes(label=as.factor(Subnum),color=as.factor(Subnum)),hjust=0.4)+
      scale_color_manual(values = colors)+
      facet_grid(Old~Stimkind)+
      # geom_hline(aes(yintercept = wtupper),mean_wt)+
      # geom_hline(aes(yintercept = wtlower),mean_wt)+
      guides(color=FALSE)+
      ggtitle(paste(" Error-",condi, "exclude:", exclude))
  }
  
  return(p)
}


```

## Cleanold
```{r}
Clean_old(d,c(),condi="MIX",is.rt=1)
Clean_old(d,c(),condi="MIX",is.rt=0)

Clean_old(d,c(),condi="MIX2",is.rt=1)
Clean_old(d,c(),condi="MIX2",is.rt=0)

```

## cleanss
```{r}
Clean_ss(d,c(),condi="MIX",is.rt=1)
Clean_ss(d,c(),condi="MIX",is.rt=0)

excl=c(11,35,13)
excl=c()
Clean_ss(d,excl,condi="MIX2",is.rt=1)
Clean_ss(d,excl,condi="MIX2",is.rt=0)

```


## Cleaning
```{r}
Clean_func(d,c(),condi="MIX",is.rt=1)
Clean_func(d,exclude = c(),condi="MIX",is.rt=0)

Clean_func(d,c(),condi="MIX2",is.rt=1)
Clean_func(d,exclude = c(),condi="MIX2",is.rt=0)

```

## Clean plot

```{r}
for(i in levels(d$FileCondi)){
  condiname = i
print(Clean_func(d,c(),condi=condiname,is.rt=1))
print(Clean_func(d,c(),condi=condiname,is.rt=0))
}

```

```{r}
dc = d %>% filter(! (FileCondi=="MIX" & Subnum %in% c(2,6,19,30)),
                  ! (FileCondi=="MIX2" & Subnum %in% c(11,22,29,32)),#c(11,13,9,35)),
                  ! (FileCondi=="ANpure" & Subnum %in% c(20,27,35,32)),
                  !  (FileCondi=="CMat" & Subnum %in% c(29,3,16)),
                  ! (FileCondi == "CMpure" & Subnum %in% c(32,35)),
                  ! (FileCondi == "VMpure" & Subnum %in% c(31,4)))  
p.medianRT(dc)
p.medianRT(d,tit="original")
  
p.ER(dc)
p.ER(d,tit="original")
```


#Mean Correct RT Function

```{r}
p.meanRT=function(d,tit,filterBlock){
  tit=paste(tit, all_subnum)
  d0=d%>%filter(Block %in% filterBlock) 
  dase = d0 %>% 
  # filter(Block<=4)%>%
  group_by(FileCondi, Correctness, Old,Setsize, Stimkind) %>%
  dplyr::summarize(RTm= mean(RT),
            se =sd(RT)/sqrt(n()))
  # print(dase)
  da1se=subset(dase,Correctness==1)#;da1se
  p=ggplot(data=da1se,aes(Setsize,RTm))+
    geom_errorbar(aes(ymin=RTm-se, ymax=RTm+se), width=.2,
                 position=position_dodge(.9),alpha=0.3) +
    geom_point(aes(color=as.factor(Old),shape=as.factor(Stimkind),group=Old),size=5)+
    geom_line(aes(color=as.factor(Old),#linetype=as.factor(FileCondi),
                  group=interaction(Old,Stimkind)))+
    scale_color_manual(name="Old-New",#breaks=c(1,0),
                        labels=c(`1`="Old", `2`="New"),
                        values=c("#F23005","#CC984D"))+
    scale_shape_discrete(
      name="ProbKind",labels = c(`1`="CM",`0`="AN",`3`="VM"))+
    # scale_linetype_discrete(
    #   name="Condition")+
    ggtitle(paste("mean CorrectRT - Set Size",tit))+
       theme_bw()+
    theme(text=element_text(size=16))+
      # ylim(700,1550)+
    facet_wrap(FileCondi~.,ncol=6)
  
  return(p)
}
  
p1=p.meanRT(d," ",2:9)
```
## All B
```{r}
p1=p.meanRT(d," ",2:9);p1
```

## B 2-4
```{r}
p1_1=p.meanRT(d," ",2:4);p1_1
```

## B 5-9
```{r}
p1_2=p.meanRT(d," ",5:9);p1_2
```

## 3 plots
```{r,out.width=8,out.height=5}
p2;p3
```

#p.medianRT()
```{r}

p.medianRT=function(d,RTmethod="median_mean", tit=" ",BlockFilter=2:9){
  cols <- c(`1`=1,`0`=2,`3`=3)
  
  tit=paste(' ',all_subnum," ",tit)
  if(RTmethod == "grant_median"){
    dase = d %>% filter(Block %in% BlockFilter) %>%
      group_by(Subnum, FileCondi,Correctness,  Old,Setsize, Stimkind) %>%
      dplyr::summarize(RTmean= median(RT)) %>%
      group_by(FileCondi,Correctness,  Old,Setsize, Stimkind) %>%
      dplyr::summarize(RTm= mean(RTmean), se =sd(RTmean)/sqrt(n()))
  }else if(RTmethod == "median_mean"){
    print("dd")
    dase = d %>% filter(Block %in% BlockFilter) %>%
      group_by(Subnum, FileCondi,Correctness,  Old,Setsize, Stimkind) %>%
      dplyr::summarize(RTmean= median(RT)) %>%
      group_by(FileCondi,Correctness,  Old,Setsize, Stimkind) %>%
      dplyr::summarize(RTm= mean(RTmean), se =sd(RTmean)/sqrt(n()))
  }else if (RTmethod == "mean"){
    
  } else{}# stop("Wrong method of calculating RT input!")
  
  # print(dase)
  da1se=subset(dase,Correctness==1)#;da1se
  p=ggplot(data=da1se,aes(Setsize,RTm))+
    geom_errorbar(aes(ymin=RTm-se, ymax=RTm+se), width=.2,
                 position=position_dodge(.9),alpha=0.3) +
    geom_point(aes(color=as.factor(Old),shape=as.factor(Stimkind),group=Old),size=5)+
    geom_line(aes(color=as.factor(Old),#linetype=as.factor(FileCondi),
                  group=interaction(Old,Stimkind)))+
    scale_color_manual(name="Old-New",#breaks=c(1,0),
                        labels=c(`1`="Old", `2`="New"),
                        values=c("#F23005","#CC984D"))+
    scale_shape_discrete(
      name="ProbKind",labels = c(`1`="CM",`0`="AN",`3`="VM"))+
    ggtitle(paste("Median CorrectRT - Set Size",tit))+
       theme_bw()+
      theme(text=element_text(size=16))+
      ylim(500,1100)+
    facet_wrap(FileCondi~.,ncol=6)
  # scale_colour_manual(name="Error Bars",values=cols, guide = guide_legend(shape = NULL,colour = NULL)) + 
  # scale_shape_manual(name="Bar",values=cols, guide="none") 
  
  return(p)
}
p2=p.medianRT(d," ",2:9)
p2
```

## plots
```{r}
p2=p.medianRT(d," ",2:9);p2
```
```{r}
p2_1=p.medianRT(d,"Block2-4",2:4);p2_1
```

```{r}
p2_2=p.medianRT(d,"Block5-9",5:9);p2_2
```

```{r}
p.medianRT(d," ",2:9)
p.medianRT(d," ",2:4)
p.medianRT(d," ",5:9)
```

##p.medianRT
```{r}
p.medianRT=function(d,tit,BlockFilter){
  tit=paste(' ',all_subnum)
  dase = d %>% filter(Block %in% BlockFilter) %>%
  group_by(FileCondi,Correctness,  Old,Setsize, Stimkind) %>%
  dplyr::summarize(RTm= median(RT),
            se =sd(RT)/sqrt(n()))
  # print(dase)
  da1se=subset(dase,Correctness==1)#;da1se
  p=ggplot(data=da1se,aes(Setsize,RTm))+
    geom_errorbar(aes(ymin=RTm-se, ymax=RTm+se), width=.2,
                 position=position_dodge(.9),alpha=0.3) +
  geom_point(aes(color=as.factor(Old),shape=as.factor(Stimkind),group=Old),size=5)+
  geom_line(aes(color=as.factor(Old),#linetype=as.factor(FileCondi),
                group=interaction(Old,Stimkind)))+
  scale_color_manual(name="Old-New",#breaks=c(1,0),
                      labels=c(`1`="Old", `2`="New"),
                      values=c("#F23005","#CC984D"))+
  scale_shape_discrete(
    name="ProbKind",labels = c(`1`="CM",`0`="AN",`3`="VM"))+
  # scale_linetype_discrete(
  #   name="Condition")+
  ggtitle(paste("Median CorrectRT - Set Size",tit))+
     theme_bw()+
    theme(text=element_text(size=16))+
    # ylim(700,1550)+
  facet_wrap(FileCondi~.,ncol=6)
  
  return(p)
}


p.medianRT(d_new,"MIX",2:9)
```

#p.ER()
```{r}
p.ER=function(d,tit=" ",BlockFilter=2:9){
  tit=paste(' ',all_subnum," ",tit)
  d0= d %>% filter(Block %in% BlockFilter) %>%
    mutate(Old= as.factor(Old),
           Setsize = as.factor(Setsize),
           Stimkind= as.factor(Stimkind))
  dase= d0 %>%
    group_by(FileCondi,Old,Setsize,Stimkind) %>%
    dplyr::summarise(Error = 1-mean(Correctness), se = sd(Correctness)/sqrt(n()))
    # summarySEwithin(data=d0,measurevar = "Correctness",withinvars =
    #                      c("FileCondi","Old","Setsize","Stimkind"))
  # print(dase)
  da1se=dase
  p=ggplot(data=da1se,aes(Setsize,Error))+
    geom_errorbar(aes(ymin=(Error)-se, ymax=(Error)+se), width=.2,
                 position=position_dodge(.9),alpha=0.5) +
  geom_point(aes(color=as.factor(Old),shape=as.factor(Stimkind),group=Old),size=5)+
  geom_line(aes(color=as.factor(Old),#linetype=as.factor(FileCondi),
                group=interaction(Old,Stimkind)))+
  scale_color_manual(name="Old-New",#breaks=c(1,0),
                      labels=c(`1`="Old", `2`="New"),
                      values=c("#F23005","#CC984D"))+
  scale_shape_discrete(
    name="ProbKind",labels = c(`1`="CM",`0`="AN",`3`="VM"))+
  # scale_linetype_discrete(
  #   name="Condition")+
  ggtitle(paste("Error Rate - Set Size",tit))+
     theme_bw()+
    theme(text=element_text(size=16))+
    # ylim(0,0.25)+
  facet_wrap(FileCondi~.,ncol=6)+
    scale_y_continuous("Probability of Error",limits=c(0,0.25))
  return(p)
}
p3=p.ER(d," ",2:9)
p3
```
```{r,fig.width=10,fig.height=6}
p3;p2
```

## ALLplots
```{r}
p3=p.ER(d," ",2:9);p3

```

```{r}
p3_1=p.ER(d,"Block 2-4",2:4);p3_1
```

```{r}
p3_2=p.ER(d,"Block5-9",5:9);p3_2
```

```{r}
p.ER(d," ",2:9)
p.ER(d," ",2:4)
p.ER(d," ",5:9)
```

#p.ERdif()
```{r}
p.ERdif=function(condition,d){
  tit=paste(condition,'across Subjects',all_subnum)
  d0= d%>% filter(FileCondi==condition)
  dase=summarySEwithin(data=d0,measurevar = "Correctness",withinvars =
                         c("Subnum","Old","Setsize","Stimkind"))
  # print(dase)
  da1se=dase
  p=ggplot(data=da1se,aes(Setsize,1-Correctness))+
    geom_errorbar(aes(ymin=(1-Correctness)-se, ymax=(1-Correctness)+se), width=.2,
                 position=position_dodge(.9),alpha=0.5) +
  geom_point(aes(color=as.factor(Old),shape=as.factor(Stimkind),group=Old),size=2)+
  geom_line(aes(color=as.factor(Old),#linetype=as.factor(FileCondi),
                group=interaction(Old,Stimkind)))+
  scale_color_manual(name="Old-New",#breaks=c(1,0),
                      labels=c(`1`="Old", `2`="New"),
                      values=c("#F23005","#CC984D"))+
  scale_shape_discrete(
    name="ProbKind",labels = c(`1`="CM",`0`="AN",`3`="VM"))+
  # scale_linetype_discrete(
  #   name="Condition")+
  ggtitle(paste("Error Rate - Set Size",tit))+
     theme_bw()+
    theme(text=element_text(size=16))+
    # ylim(700,1550)+
  facet_wrap(Subnum~.)+
    scale_y_continuous("Probability of Error")+
    ylim(c(0,0.4))
  
   return (p)
}
p.ERdif("MIX2",d)
```

## ALLplots
```{r, fig.width=15,fig.height=10}

for(i in summary(d$FileCondi)%>%names){
  p=p.ERdif(i,d)
  print(p)
}

```



#p.RTdif
```{r}
p.RTdif=function(condition,d){
  tit=paste(condition,'across Subjects',all_subnum)
  
  # condition="ANpure"
  d0= d%>% filter(FileCondi==condition)
  dase=d0 %>% group_by(Subnum,Old,Setsize,Stimkind,Correctness) %>%
    dplyr::summarise(median.RT=median(RT),se=sd(RT)/sqrt(n()))

  # print(dase)
  da1se=dase %>% filter(Correctness==1)
  p=ggplot(data=da1se,aes(Setsize,median.RT))+
    geom_errorbar(aes(ymin=(median.RT)-se, ymax=(median.RT)+se), width=.2,
                 position=position_dodge(.9),alpha=0.5) +
  geom_point(aes(color=as.factor(Old),shape=as.factor(Stimkind),group=Old),size=2)+
  geom_line(aes(color=as.factor(Old),#linetype=as.factor(FileCondi),
                group=interaction(Old,Stimkind)))+
  scale_color_manual(name="Old-New",#breaks=c(1,0),
                      labels=c(`1`="Old", `2`="New"),
                      values=c("#F23005","#CC984D"))+
  scale_shape_discrete(
    name="ProbKind",labels = c(`1`="CM",`0`="AN",`3`="VM"))+
  # scale_linetype_discrete(
  #   name="Condition")+
  ggtitle(paste("RT - Set Size",tit))+
     theme_bw()+
    theme(text=element_text(size=16))+
    # ylim(700,1550)+
  facet_wrap(Subnum~.)+
    scale_y_continuous("Response Time")+
    ylim(c(0,3500))
  
   return (p)
}
p.RTdif("ANpure",subset(d,Subnum==32))
# p.RTdif
```
## Plot
```{r, fig.width=10,fig.height=10}

for(i in summary(d$FileCondi)%>%names){
   i="MIX"
  p=p.RTdif(i,d)
  print(p)
   break
}

```
#p.crossblockER
```{r}
p.crossblockER=function(d,tit,CondiFilter){
  tit=paste(' ',all_subnum," ",tit)
  d0= d %>% 
    mutate(Block=paste("Block",Block,sep=""))%>%
    filter(FileCondi %in% CondiFilter)
  dase=summarySEwithin(data=d0,measurevar = "Correctness",withinvars =
                         c("FileCondi","Old","Setsize","Stimkind","Block"))
  # print(dase)
  da1se=dase
  p=ggplot(data=da1se,aes(Setsize,1-Correctness))+
    geom_errorbar(aes(ymin=(1-Correctness)-se, ymax=(1-Correctness)+se), width=.2,
                 position=position_dodge(.9),alpha=0.5) +
  geom_point(aes(color=as.factor(Old),shape=as.factor(Stimkind),group=Old),size=2)+
  geom_line(aes(color=as.factor(Old),#linetype=as.factor(FileCondi),
                group=interaction(Old,Stimkind)))+
  scale_color_manual(name="Old-New",#breaks=c(1,0),
                      labels=c(`1`="Old", `2`="New"),
                      values=c("#F23005","#CC984D"))+
  scale_shape_discrete(
    name="ProbKind",labels = c(`1`="CM",`0`="AN",`3`="VM"))+
  # scale_linetype_discrete(
  #   name="Condition")+
  ggtitle(paste("Error Rate - Set Size",tit))+
     theme_bw()+
    theme(text=element_text(size=16))+
    ylim(0,0.25)+
  facet_wrap(FileCondi~Block,ncol=4)+
    scale_y_continuous("Probability of Error")
  return(p)
}

p.crossblockER(d," ",c("MIX","MIX2"))

p.crossblockRT=function(d,tit,CondiFilter){
    # CondiFilter=c("MIX","MIX2");tit="1"
  tit=paste(' ',all_subnum," ",tit)
  dase = d %>%
    mutate(Block=paste("Block",Block,sep=""))%>%
    
    filter(as.factor(FileCondi) %in% CondiFilter) %>%
  group_by(FileCondi,Correctness,  Old,Setsize, Stimkind, Block) %>%
  dplyr::summarize(RTm= median(RT),
            se =sd(RT)/sqrt(n()))
  # print(dase)
  da1se=subset(dase,Correctness==1)#;da1se
  p=ggplot(data=da1se,aes(Setsize,RTm))+
    geom_errorbar(aes(ymin=RTm-se, ymax=RTm+se), width=.2,
                 position=position_dodge(.9),alpha=0.3) +
  geom_point(aes(color=as.factor(Old),shape=as.factor(Stimkind),group=Old),size=2)+
  geom_line(aes(color=as.factor(Old),#linetype=as.factor(FileCondi),
                group=interaction(Old,Stimkind)))+
  scale_color_manual(name="Old-New",#breaks=c(1,0),
                      labels=c(`1`="Old", `2`="New"),
                      values=c("#F23005","#CC984D"))+
  scale_shape_discrete(
    name="ProbKind",labels = c(`1`="CM",`0`="AN",`3`="VM"))+
  # scale_linetype_discrete(
  #   name="Condition")+
  ggtitle(paste("Median CorrectRT - Set Size",tit))+
     theme_bw()+
    theme(text=element_text(size=16))+
    ylim(500,1100)+
  facet_wrap(FileCondi~Block,ncol=4)
  
  return(p)
}
p.crossblockRT(d," ",c("MIX","MIX2"))
```


# Check for concern
```{r}
p.RTdif0=function(condition,d){
  tit=paste(condition,'across Subjects',all_subnum)
  
  # condition="ANpure"
  d0= d%>% filter(FileCondi==condition)
  dase=d0 %>% group_by(Subnum,Setsize,Stimkind,Correctness) %>%
    dplyr::summarise(median.RT=median(RT),se=sd(RT)/sqrt(n()))

  # print(dase)
  da1se=dase %>% filter(Correctness==1)
  p=ggplot(data=da1se,aes(Setsize,median.RT))+
    geom_errorbar(aes(ymin=(median.RT)-se, ymax=(median.RT)+se), width=.2,
                 position=position_dodge(.9),alpha=0.5) +
  geom_point(aes(shape=as.factor(Stimkind)),size=2)+
  geom_line(aes(#linetype=as.factor(FileCondi),
                group=Stimkind))+
  
  scale_shape_discrete(
    name="ProbKind",labels = c(`1`="CM",`0`="AN",`3`="VM"))+
  # scale_linetype_discrete(
  #   name="Condition")+
  ggtitle(paste("RT - Set Size",tit))+
     theme_bw()+
    theme(text=element_text(size=16))+
    # ylim(700,1550)+
  facet_wrap(Subnum~.)+
    scale_y_continuous("Response Time")+
    ylim(c(450,1500))
  
   return (p)
}

p.ERdif0=function(condition,d){
  tit=paste(condition,'across Subjects',all_subnum)
  d0= d%>% filter(FileCondi==condition)
  dase=summarySEwithin(data=d0,measurevar = "Correctness",withinvars =
                         c("Subnum","Setsize","Stimkind"))
  # print(dase)
  da1se=dase
  p=ggplot(data=da1se,aes(Setsize,1-Correctness))+
    geom_errorbar(aes(ymin=(1-Correctness)-se, ymax=(1-Correctness)+se), width=.2,
                 position=position_dodge(.9),alpha=0.5) +
  geom_point(aes(shape=as.factor(Stimkind)),size=2)+
  geom_line(aes(#linetype=as.factor(FileCondi),
                group=Stimkind))+
  scale_shape_discrete(
    name="ProbKind",labels = c(`1`="CM",`0`="AN",`3`="VM"))+

  ggtitle(paste("Error Rate - Set Size",tit))+
     theme_bw()+
    theme(text=element_text(size=16))+
    # ylim(700,1550)+
  facet_wrap(Subnum~.)+
    scale_y_continuous("Probability of Error")+
    ylim(c(0,0.6))
  
   return (p)
}
d_new=d%>%
  # group_by()%>%
  mutate(Stimkind=case_when(
    Stimkind == 0 & Old==2 ~ "AN_new",
    TRUE ~ "Mean of Other Conditions"
  ))
p.RTdif0("MIX",d_new)
p.ERdif0("MIX",d_new)
```
## get sub11,sub12
```{r}
d_2sub=d%>%filter(Subnum %in% c(11,12))
# p.RTdif("MIX",d_2sub)
p.medianRT(d%>%filter((!Subnum %in% c(11,12)) & FileCondi=="MIX" ),"Excluded sub11,12",2:9)
p.medianRT(d%>%filter((!Subnum %in% c(11,12))  ),"Excluded sub11,12",2:9)
```

## Redo ERp
```{r}
p.ER2=function(d,tit,BlockFilter){
  tit=paste(' ',all_subnum," ",tit)
  d0= d %>% filter(Block %in% BlockFilter)
  dase=d%>% group_by(FileCondi,Old,Setsize,Stimkind)%>%
    dplyr::summarise(ER=mean(abs(1-Correctness)),se=sd(abs(1-Correctness))/sqrt(n()))
  
  
  da1se=dase
  p=ggplot(data=da1se,aes(Setsize,ER))+
    geom_errorbar(aes(ymin=ER-se, ymax=ER+se), width=.2,
                 position=position_dodge(.9),alpha=0.5) +
  geom_point(aes(color=as.factor(Old),shape=as.factor(Stimkind),group=Old),size=5)+
  geom_line(aes(color=as.factor(Old),#linetype=as.factor(FileCondi),
                group=interaction(Old,Stimkind)))+
  scale_color_manual(name="Old-New",#breaks=c(1,0),
                      labels=c(`1`="Old", `2`="New"),
                      values=c("#F23005","#CC984D"))+
  scale_shape_discrete(
    name="ProbKind",labels = c(`1`="CM",`0`="AN",`3`="VM"))+
  # scale_linetype_discrete(
  #   name="Condition")+
  ggtitle(paste("Error Rate - Set Size",tit))+
     theme_bw()+
    theme(text=element_text(size=16))+
    # ylim(700,1550)+
  facet_wrap(FileCondi~.,ncol=6)+
    scale_y_continuous("Probability of Error")
  return(p)
}
p3=p.ER2(d," ",2:9);p3


# abs(-1)
```






# View all plot
```{r,fig.width=15,fig.height=10}
p1;p2;p3
```
```{r}
names(d)
```

# Violence plot

```{r}


p <- d %>% filter(FileCondi=="ANpure")%>%
  plot_ly(
    x = ~Setsize,
    y = ~RT,
    split = ~Setsize,
    type = 'violin',
    box = list(
      visible = T
    ),
    meanline = list(
      visible = T
    )
  ) %>% 
  layout(
    xaxis = list(
      title = "Setsize"
    ),
    yaxis = list(
      title = "RT",
      zeroline = F
    )
  )
p

```

```{r}
p <- d %>%
  plot_ly(type = 'violin') %>%
  add_trace(
    x = ~FileCondi[d$Stimkind ==1],
    y = ~RT[d$Stimkind == 1],
    legendgroup = 'Yes',
    scalegroup = 'Yes',
    name = 'Yes',
    side = 'negative',
    box = list(
      visible = T
    ),
    meanline = list(
      visible = T
    ),
    line = list(
      color = 'blue'
    )
  ) %>%
  add_trace(
    x = ~FileCondi[d$Stimkind ==0],
    y = ~RT[d$Stimkind == 0],
    legendgroup = 'No',
    scalegroup = 'No',
    name = 'No',
    side = 'positive',
    box = list(
      visible = T
    ),
    meanline = list(
      visible = T
    ),
    line = list(
      color = 'green'
    )
  ) %>% 
  layout(
    xaxis = list(
      title = ""  
    ),
    yaxis = list(
      title = "",
      zeroline = F
    ),
    violingap = 0,
    violingroupgap = 0,
    violinmode = 'overlay'
  )

p
```


# Investegate median/mean
```{r}
dnew=d %>% filter(FileCondi=="ANpure",Setsize==2) %>%
  mutate(Old=as.factor(Old))

ggplot(dnew, aes(x=RT, color=FileCondi,fill=FileCondi)) +
  geom_density(alpha=0.2)+
  # xlim(0,4000)+
  facet_wrap(.~Subnum)
```


#Check mix-4
```{r}
d%>%filter(FileCondi=="MIX2",Subnum>=15)%>%
  group_by(Old,Side) %>%
  dplyr::summarise(n=n())
d%>%filter(FileCondi=="MIX2")%>%
  group_by(Stimkind,Old,Side,Subnum) %>%
  dplyr::summarise(n=n())


d%>%filter(FileCondi=="MIX",Subnum>=15)%>%
  group_by(Stimkind) %>%
  dplyr::summarise(n=n())
d%>%filter(FileCondi=="MIX",Subnum>=15)%>%
  group_by(Stimkind,Old,Side) %>%
  dplyr::summarise(n=n())
#from subnum=15, things start to go right
d%>%filter(FileCondi=="MIX2",Subnum>14)%>%
  filter(Stimkind==1)%>%
  select(Subnum,Old,Side,WhichProbe,Stimkind)%>%
  mutate(Old = case_when(Old==1 ~ "Old",
                         Old==2 ~ "New"),
         Side= case_when(Side==0 ~ "Left",
                         Side==1 ~ "Right"))%>%
  mutate(check = case_when(
    Old=="New" & Side=="Right" & WhichProbe< 5 ~ "T",
    Old=="New" & Side=="Left"  & WhichProbe>=5 ~ "T",
    Old=="Old" & Side=="Right" & WhichProbe>=5 ~ "T",
    Old=="Old" & Side=="Left"  & WhichProbe< 5 ~ "T",
    TRUE ~ 'F')) %>% arrange(Subnum,Old)
```



#Add name function
```{r}
MutateName=function(d){
  d%>%
    filter(Subnum>15)%>%
      mutate(Old=case_when(Old==1~"Old",
                           Old==2~"New"),
             Side=case_when(Side==0~"left",
                            Side==1~"Right"),
             Stimkind=case_when(Stimkind==1~"CM",
                                Stimkind==0~"AN",
                                Stimkind==2~"VM")
             )
}
```

#Write csv
```{r}
write.csv(file="Alldata2.csv",d)
d%>%filter(FileCondi=="MIX")
```


##check manipulation
```{r}
MutateName(d)%>%
  group_by(FileCondi,Old,Side,Stimkind)%>%
  dplyr::summarise(n())
d$FileCondi%>%summary
```

```{r}
MutateName(d)%>%
  group_by(FileCondi,Old,Side)%>%
  dplyr::summarise(n())
```


## Plot names
```{r}
p.medianRT(d_my,"mydata",2:8)
p.ER(d_my,"mydata",2:8)

```

##check left_right side
```{r}
p.medianRT(d%>%filter(Side==0),"Left side",2:9) 
p.medianRT(d%>%filter(Side==1),"Right side",2:9) 

p.ER(d%>%filter(Side==0),"Left side",2:9) 
p.ER(d%>%filter(Side==1),"Right side",2:9) 


```
#p.serposeRT
```{r}
# p.medianRT(d%>%filter(FileCondi=="MIX"),"",2:9) 
p.serposeRT=function(d,tit,BlockFilter){
  tit=paste(' ',all_subnum," ",tit)
  dase = d %>% filter(Block %in% BlockFilter) %>%
    mutate(Setsize=paste("Setsize",Setsize))%>%
  group_by(Correctness, Setsize, Stimkind,Lag,FileCondi) %>%
  dplyr::summarize(RTmedian= median(RT),
            se =sd(RT)/sqrt(n()))
  # print(dase)
  da1se=subset(dase,Correctness==1)#;da1se
  p=ggplot(data=da1se,aes(Lag,RTmedian))+
    geom_errorbar(aes(ymin=RTmedian-se, ymax=RTmedian+se), width=.2,
                 position=position_dodge(.9),alpha=0.3) +
  geom_point(aes(shape=as.factor(Stimkind)),size=2,alpha=0.4)+
  geom_line(aes(linetype=as.factor(Stimkind),
                group=Stimkind))+
  scale_shape_discrete(
    name="ProbKind",labels = c(`1`="CM",`0`="AN",`3`="VM"))+
  scale_linetype_discrete(
    name="ProbKind",labels = c(`1`="CM",`0`="AN",`3`="VM"))+
  # scale_linetype_discrete(
  #   name="Condition")+
  ggtitle(paste("Lag-RT across Setsize",tit))+
     theme_bw()+
    theme(text=element_text(size=12))+
    ylim(500,1100)+
  facet_wrap(Setsize~FileCondi,ncol=6)
  
  return(p)
}
p.serposeRT(subset(d,Old==1),"For old items",2:9)


p.serposeER=function(d,tit,BlockFilter){
  tit=paste(' ',all_subnum," ",tit)
  dase = d %>% filter(Block %in% BlockFilter) %>%
    mutate(Setsize=paste("Setsize",Setsize))%>%
  group_by(Setsize, Stimkind,Lag,FileCondi) %>%
  dplyr::summarize(ER= 1-mean(Correctness),
            se =sd(Correctness)/sqrt(n()))
  # print(dase)
  da1se=dase
  p=ggplot(data=da1se,aes(Lag,ER))+
    geom_errorbar(aes(ymin=ER-se, ymax=ER+se), width=.2,
                 position=position_dodge(.9),alpha=0.3) +
  geom_point(aes(shape=as.factor(Stimkind)),size=2,alpha=0.4)+
  geom_line(aes(linetype=as.factor(Stimkind),
                group=Stimkind))+
  # scale_color_manual(name="Old-New",#breaks=c(1,0),
  #                     labels=c(`1`="Old", `2`="New"),
  #                     values=c("#F23005","#CC984D"))+
  scale_shape_discrete(
    name="ProbKind",labels = c(`1`="CM",`0`="AN",`3`="VM"))+
  scale_linetype_discrete(
    name="ProbKind",labels = c(`1`="CM",`0`="AN",`3`="VM"))+
  # scale_linetype_discrete(
  #   name="Condition")+
  ggtitle(paste("Lag-ER",tit))+
     theme_bw()+
    theme(text=element_text(size=12))+
    # ylim(500,10120)+
  facet_wrap(Setsize~FileCondi,ncol=6)
  
  return(p)
}
p.serposeER(subset(d,Old==1),"For cleaned data",2:9)

# 
# p.ER(d%>%filter(Side==0),"Left side",2:9) 
# p.ER(d%>%filter(Side==1),"Right side",2:9) 

```



##t-test for left/right side
```{r}
d%>%
  # filter(FileCondi=="MIX2")%>%
  group_by(Side)%>%dplyr::summarise(meanrt=mean(RT),se=sd(RT)/sqrt(n()),
                                      n=n(),
                                      up=meanrt+se*qt(0.025,n),low=meanrt-se*qt(0.025,n))
# qt(0.025,11924)

```





# show color
```{r}
for (i in 1:19){
  print(wes_palette(names(wes_palettes[i])))
}
```





















